---
title: "Extracted Data Part 3"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,warning = FALSE,results='hide')

# Load the packages
library(data.table)
library(stringr)
library(splitstackshape)
library(pdftools)

# load the data
load("Oneuseful3.RData")
```

# Useful Data-frame

This table is a mock representation of how an entire district results can be represented 
with all the necessary information. In the tables Yes means the value exists and No means
the cell is empty.

Clearly the percentage values for Postal District Votes and Final District Results are not 
calculated. Also Displaced District Votes does not have percentage values as well. These
calculations are different than previous situations. Yet they are done without any hustle.

## Format of Data-frame for 2005

Year 2005 is singularly the worst with a lot of missing values.

|          ColNames         | Electorate 1 | Electorate 1 | Electorate ... | Electorate ... | Postal District  Votes | Postal District  Votes | Final District  Results | Final District  Results |
|:-------------------------:|:------------:|:------------:|:--------------:|:--------------:|:----------------------:|:----------------------:|:-----------------------:|:-----------------------:|
|                           |     Votes    |  Percentage  |      Votes     |   Percentage   |          Votes         |       Percentage       |          Votes          |        Percentage       |
|      Candidate Name 1     |       Yes    |     Yes      |     Yes        |     Yes        |       Yes              |         No             |           Yes           |         No              |
|     Candidate Name ...    |       Yes    |     Yes      |     Yes        |     Yes        |       Yes              |         No             |           Yes           |         No              |
|  Total No of Valid Votes  |       Yes    |     Yes      |     Yes        |     Yes        |       Yes              |         No             |           Yes           |         No              |
|   No of  Rejected Votes   |       Yes    |     Yes      |     Yes        |     Yes        |       Yes              |         No             |           Yes           |         No              |
|  Total No of Votes Polled |       Yes    |     Yes      |     Yes        |     Yes        |       Yes              |         No             |           Yes           |         No              |
| No of Registered Electors |       Yes    |     No       |     Yes        |     No         |       No               |         No             |           Yes           |         No              |


## Rectify Data-frame for 2005

Two functions developed to resolve the percentage calculations and successfully
done as below mentioned code chunk. 

```{r Rectify 2005}
# adding percentage values for Final District Results
# and Postal District Votes when district is given
FixPercent<-function(Dis,Ele)
{  
if(Ele==TRUE)
  {  
  # Selecting Final District Results 
  data<-Election2005[Electorate=="Final District Results" & District==Dis]
  # calculating percentages
  for(i in 1:(dim(data)[1]-2))
      {
      data[i,6]<-round((100*data[i,5])/data[(dim(data)[1]-1),5],2)
      }
      data[dim(data)[1]-1,6]<-round((100*data[(dim(data)[1]-1),5])/data[dim(data)[1],5],2)
    return(data)    
  }
else
  {
  # Selecting Postal District Votes 
  data<-Election2005[Electorate=="Postal District Votes" & District==Dis]
  # calculating percentages
  for(i in 1:(dim(data)[1]-2))
      {
      data[i,6]<-round((100*data[i,5])/data[(dim(data)[1]-1),5],2)
      }
  return(data)
  }
}
# Obtaining the districts
data<-unique(Election2005$District)

# creating empty data-set
datas<-NULL

# calculating the percentage values
# for Final District Results and 
# Postal District Votes
for (i in 1:length(data)) 
{
datas[[i]]<-FixPercent(Dis = data[i],Ele = TRUE)  
datas[[i+22]]<-FixPercent(Dis = data[i],Ele = FALSE)
}

# adding percentage values for Displaced District Votes
FixPercentD<-function(Dis)
{  
  # Selecting Final District Results 
  data<-Election2005[Electorate=="Displaced District Votes" & District==Dis]
  # calculating percentages
  for(i in 1:(dim(data)[1]-2))
      {
      data[i,6]<-round((100*data[i,5])/data[(dim(data)[1]-1),5],2)
      }
  return(data)
}

# calculating percentage values for the three displaced 
# districts
datas[[45]]<-FixPercentD("Jaffna")
datas[[46]]<-FixPercentD("Vanni")
datas[[47]]<-FixPercentD("Trincomalee")

# combining the lists into one data-frame
Temp<-do.call("rbind",datas)

# replacing the calculated percentages with their 
# respective observations
Election2005[(Electorate=="Displaced District Votes" | 
              Electorate=="Final District Results" |
              Electorate=="Postal District Votes")]<-Temp
# removing rows with percentages and votes being zero 
Election2005<-Election2005[!(Electorate=="Postal District Votes" & 
                            ColNames=="No of Registered Electors" | 
                            Electorate=="Displaced District Votes" &
                            ColNames=="No of Registered Electors")]
```

# Useful Data-frames

The data-frame looks fine, now is the final stage of exporting the data-frame 
as a csv file.

```{r Export csv file}
write.csv(Election2005, file = "Election2005.csv")
```

*THANK YOu*
