---
title: "Extracted Data Part 2"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,warning = FALSE,results='hide')

# Load the packages
library(data.table)
library(stringr)
library(splitstackshape)
library(pdftools)

# load the data
load("Oneuseful1.RData")
```

There are three types of table information for votes and percentages. Below is on of the three tables
explaining them clearly. It should be noted that these are mock tables. Most of the issues 
occur with related to Postal District Votes. In year 2005 there are lot of missing values
that needs to be calculated. 

Each table is a mock representation of how an entire district results can be represented 
with all the necessary information. In the tables Yes means the value exists and No means
the cell is empty.

# Format of Data-frame for 1982,1988 and 1999

The years 1982, 1988 and 1999 have the same format. Just two values different from 
the next table format, and that table is much more full. 

|          ColNames         | Electorate 1 | Electorate 1 | Electorate ... | Electorate ... | Postal District  Votes | Postal District  Votes | Final District  Results | Final District  Results |
|:-------------------------:|:------------:|:------------:|:--------------:|:--------------:|:----------------------:|:----------------------:|:-----------------------:|:-----------------------:|
|                           |     Votes    |  Percentage  |      Votes     |   Percentage   |          Votes         |       Percentage       |          Votes          |        Percentage       |
|      Candidate Name 1     |       Yes    |     Yes      |     Yes        |     Yes        |       Yes              |         Yes            |           Yes           |         Yes             |
|     Candidate Name ...    |       Yes    |     Yes      |     Yes        |     Yes        |       Yes              |         Yes            |           Yes           |         Yes             |
|  Total No of Valid Votes  |       Yes    |     Yes      |     Yes        |     Yes        |       Yes              |         Yes            |           Yes           |         Yes             |
|   No of  Rejected Votes   |       Yes    |     Yes      |     Yes        |     Yes        |       Yes              |         Yes            |           Yes           |         Yes             |
|  Total No of Votes Polled |       Yes    |     Yes      |     Yes        |     Yes        |       Yes              |         No             |           Yes           |         Yes             |
| No of Registered Electors |       Yes    |     No       |     Yes        |     No         |       No               |         No             |           Yes           |         No              |

# Rectify Votes and Percentages 

## Rectify Data-frame for 1982

Two percentages are not possible practically. They are resolved below.
Several missing vote values should be replaced by 0.

```{r Rectify 1982}
# Removing the Postal District Votes for No of Registered Electors rows
Election1982 <-Election1982[!(Election1982$ColNames=="No of Registered Electors" & 
                              Election1982$Electorate=="Postal District Votes" & 
                              is.na(Election1982$Votes)),]

# It seems the total of walapane electorate should be 34120 not 24120
Election1982$Votes[Election1982$District=="Nuwara-Eliya" & 
                   Election1982$Electorate=="Walapane" & 
                   Election1982$ColNames=="Total No of Votes Polled"]<-34120  
# So the percentage also changes   
Election1982$Percentage[Election1982$District=="Nuwara-Eliya" & 
                        Election1982$Electorate=="Walapane" & 
                        Election1982$ColNames=="Total No of Votes Polled"]<-round(3412000/38414,2)
# There cannot be an percentage for 139.81, which is not possible
Election1982$Percentage[Election1982$District=="Nuwara-Eliya" & 
                        Election1982$Electorate=="Walapane" & 
                        Election1982$ColNames=="Total No of Valid Votes"]<-round(3372300/34120,2)
# This means We have to change the total for Nuwara-Eliya District as well,
# which means from 164817 to 174817
Election1982$Votes[Election1982$District=="Nuwara-Eliya" & 
                   Election1982$Electorate=="Final District Results" & 
                   Election1982$ColNames=="Total No of Votes Polled"]<-174817

# setting missing votes values as zeros
Election1982$Votes[is.na(Election1982$Votes)]<-0

# Also the kandy district teldeniya electorate has a percentage value for 867.38
# So the value 3145 for Registered electors should be 31145 which would
# make the total value of Registered Electors from 536767 to 564767

# Change from 3145 to 31145
Election1982$Votes[Election1982$District=="Mahanuwara" & 
                   Election1982$Electorate=="Teldeniya" & 
                   Election1982$ColNames=="No of Registered Electors"]<-31145

# Change from 536767 to 564767
Election1982$Votes[Election1982$District=="Mahanuwara" & 
                   Election1982$Electorate=="Final District Results" & 
                   Election1982$ColNames=="No of Registered Electors"]<-564767
# Change the Percentage from 867.38
Election1982$Percentage[Election1982$District=="Mahanuwara" & 
                        Election1982$Electorate=="Teldeniya" & 
                        Election1982$ColNames=="Total No of Votes Polled"]<-round(2727900/31145,2)

```

## Ensure if Still Tallying of District and Electorate votes are Equal for Year 1982  

```{r Ensure 1982 is okay}
# Extracting only Final District Results of 
# Number of Registered Electors
# and then adding all the votes 
ElecFinal1982<-subset(Election1982,Electorate=="Final District Results" 
                      & ColNames=="No of Registered Electors")
# added votes will be cross checked with the pdf document
ElecFinal1982[,sum(Votes),by="ColNames"]

# Extracting except Final District Results of 
# Number of Registered Electors
# and then adding all the votes 
ElecFinal1982<-subset(Election1982,Electorate!="Final District Results" 
                      & ColNames=="No of Registered Electors")
# added votes will be cross checked with the pdf document
ElecFinal1982[,sum(Votes),by="ColNames"]

# Extracting only Final District Results of 
# Total Polled
# and then adding all the votes 
ElecFinal1982<-subset(Election1982,Electorate=="Final District Results" 
                      & ColNames=="Total No of Votes Polled")
# added votes will be cross checked with the pdf document
ElecFinal1982[,sum(Votes),by="ColNames"]

# Extracting except Final District Results of 
# Total Polled
# and then adding all the votes 
ElecFinal1982<-subset(Election1982,Electorate!="Final District Results" 
                      & ColNames=="Total No of Votes Polled")
# added votes will be cross checked with the pdf document
ElecFinal1982[,sum(Votes),by="ColNames"]

# Extracting only Final District Results of 
# No of Rejected Votes
# and then adding all the votes 
ElecFinal1982<-subset(Election1982,Electorate=="Final District Results" 
                      & ColNames=="No of Rejected Votes")
# added votes will be cross checked with the pdf document
ElecFinal1982[,sum(Votes),by="ColNames"]

# Extracting except Final District Results of 
# No of Rejected Votes
# and then adding all the votes 
ElecFinal1982<-subset(Election1982,Electorate!="Final District Results" 
                      & ColNames=="No of Rejected Votes")
# added votes will be cross checked with the pdf document
ElecFinal1982[,sum(Votes),by="ColNames"]

# Extracting only Final District Results of 
# No of Valid Votes
# and then adding all the votes 
ElecFinal1982<-subset(Election1982,Electorate=="Final District Results" 
                      & ColNames=="Total No of Valid Votes")
# added votes will be cross checked with the pdf document
ElecFinal1982[,sum(Votes),by="ColNames"]

# Extracting except Final District Results of 
# No of Valid Votes
# and then adding all the votes 
ElecFinal1982<-subset(Election1982,Electorate!="Final District Results" 
                      & ColNames=="Total No of Valid Votes")
# added votes will be cross checked with the pdf document
ElecFinal1982[,sum(Votes),by="ColNames"]

# Extracting only Final District Results of 
# Mr.J.R. Jayawardene
# and then adding all the votes 
ElecFinal1982<-subset(Election1982,Electorate=="Final District Results" 
                      & ColNames=="Mr.J.R. Jayawardene")
# added votes will be cross checked with the pdf document
ElecFinal1982[,sum(Votes),by="ColNames"]

# Extracting except Final District Results of 
# Mr.J.R. Jayawardene
# and then adding all the votes 
ElecFinal1982<-subset(Election1982,Electorate!="Final District Results" 
                      & ColNames=="Mr.J.R. Jayawardene")
# added votes will be cross checked with the pdf document
ElecFinal1982[,sum(Votes),by="ColNames"]

# Extracting only Final District Results of 
# Mr.H.S.R.B.K. Kobbekaduwa
# and then adding all the votes 
ElecFinal1982<-subset(Election1982,Electorate=="Final District Results" 
                      & ColNames=="Mr.H.S.R.B.K. Kobbekaduwa")
# added votes will be cross checked with the pdf document
ElecFinal1982[,sum(Votes),by="ColNames"]

# Extracting except Final District Results of 
# Mr.H.S.R.B.K. Kobbekaduwa
# and then adding all the votes 
ElecFinal1982<-subset(Election1982,Electorate!="Final District Results" 
                      & ColNames=="Mr.H.S.R.B.K. Kobbekaduwa")
# added votes will be cross checked with the pdf document
ElecFinal1982[,sum(Votes),by="ColNames"]

# Extracting only Final District Results of 
#  Mr. Rohana Wijeweera 
# and then adding all the votes 
ElecFinal1982<-subset(Election1982,Electorate=="Final District Results" 
                      & ColNames=="Mr. Rohana Wijeweera")
# added votes will be cross checked with the pdf document
ElecFinal1982[,sum(Votes),by="ColNames"]

# Extracting except Final District Results of 
# Mr. Rohana Wijeweera 
# and then adding all the votes 
ElecFinal1982<-subset(Election1982,Electorate!="Final District Results" 
                      & ColNames=="Mr. Rohana Wijeweera")
# added votes will be cross checked with the pdf document
ElecFinal1982[,sum(Votes),by="ColNames"]

# Extracting only Final District Results of 
#  Mr. G.G. Ponnambalam 
# and then adding all the votes 
ElecFinal1982<-subset(Election1982,Electorate=="Final District Results" 
                      & ColNames=="Mr.G.G. Ponnambalam")
# added votes will be cross checked with the pdf document
ElecFinal1982[,sum(Votes),by="ColNames"]

# Extracting except Final District Results of 
# Mr. G.G. Ponnambalam
# and then adding all the votes 
ElecFinal1982<-subset(Election1982,Electorate!="Final District Results" 
                      & ColNames=="Mr.G.G. Ponnambalam")
# added votes will be cross checked with the pdf document
ElecFinal1982[,sum(Votes),by="ColNames"]

# Extracting only Final District Results of 
# Dr. Colvin R. De Silva 
# and then adding all the votes 
ElecFinal1982<-subset(Election1982,Electorate=="Final District Results" 
                      & ColNames=="Dr. Colvin R. De Silva")
# added votes will be cross checked with the pdf document
ElecFinal1982[,sum(Votes),by="ColNames"]

# Extracting except Final District Results of 
# Dr. Colvin R. De Silva 
# and then adding all the votes 
ElecFinal1982<-subset(Election1982,Electorate!="Final District Results" 
                      & ColNames=="Dr. Colvin R. De Silva")
# added votes will be cross checked with the pdf document
ElecFinal1982[,sum(Votes),by="ColNames"]

# Extracting only Final District Results of 
# Mr. Vasudeva Nanayakakra 
# and then adding all the votes 
ElecFinal1982<-subset(Election1982,Electorate=="Final District Results" 
                      & ColNames=="Mr. Vasudeva Nanayakkara")
# added votes will be cross checked with the pdf document
ElecFinal1982[,sum(Votes),by="ColNames"]

# Extracting except Final District Results of 
# Mr. Vasudeva Nanayakakra 
# and then adding all the votes 
ElecFinal1982<-subset(Election1982,Electorate!="Final District Results" 
                      & ColNames=="Mr. Vasudeva Nanayakkara")
# added votes will be cross checked with the pdf document
ElecFinal1982[,sum(Votes),by="ColNames"]
```

So now the Totals have changed  and below is the final tally :

1. No of Registered Electors : 8144992
2. Total No of Valid Votes : 6522153
3. No of Rejected Votes : 80500
4. Total No of Polled Votes : 6602617
5. Mr.J.R. Jayawardene : 3450815
6. Mr.H.S.R.B.K. Kobbekaduwa : 2546438	
7. Mr. Rohana Wijeweera : 273428
8. Mr.G.G. Ponnambalam : 173934
9. Dr. Colvin R. De Silva : 58095
10. Mr. Vasudeva Nanayakkara : 16995

## Rectify Data-frame for 1988

There are three vote values but they do not have any percentages represented
for them. They are rectified. Further few Percentages and votes are replaced
from Missing values to 0. Also there cannot be a percentage of 9077.37, that
is also recalculated.

```{r Rectify 1988}
# Removing the Postal District Votes for No of Registered Electors rows
Election1988<-Election1988[!(Election1988$ColNames=="No of Registered Electors" & 
                             Election1988$Electorate=="Postal District Votes" & 
                             is.na(Election1988$Votes)),]

# Even though there are 246 valid votes it does not represent by a percentage of 
# Registered Electors, that is rectified
Election1988$Percentage[Election1988$ColNames=="Total No of Valid Votes" & 
                        Election1988$Electorate=="Postal District Votes" &
                        Election1988$District=="Trincomalee"]<-round(24600/251,2)

# Even though there are 81949 Polled votes it does not represent by a percentage of 
# Registered Electors, that is rectified
Election1988$Percentage[Election1988$ColNames=="Total No of Votes Polled" & 
                        Election1988$Electorate=="Final District Results" &
                        Election1988$District=="Trincomalee"]<-round(8194900/152289,2)

# Even though there are 137718 Polled votes it does not represent by a percentage of 
# Registered Electors, that is rectified
Election1988$Percentage[Election1988$ColNames=="Total No of Votes Polled" & 
                        Election1988$Electorate=="Final District Results" &
                        Election1988$District=="Badulla"]<-round(13771800/329462,2)

# setting missing votes values as zeros
Election1988$Percentage[is.na(Election1988$Votes) & Election1988$ColNames!="Total No of Votes Polled"]<-0
Election1988$Votes[is.na(Election1988$Votes)]<-0

# Even though there are 388602 Valid votes it represents by a percentage of 
# Registered Electors which is impossible(9077.37%), that is rectified
Election1988$Percentage[Election1988$ColNames=="Total No of Valid Votes" & 
                        Election1988$Electorate=="Final District Results" &
                        Election1988$District=="Kurunegala"]<-round(38860200/392883,2)

# Even though there are 49613 Polled votes it is not represented by a percentage of 
# Registered Electors, that is rectified
Election1988$Percentage[Election1988$ColNames=="Total No of Votes Polled" & 
                        Election1988$Electorate=="Baddegama" &
                        Election1988$District=="Galle"]<-round(4916300/65351,2)
```

## Ensure if Still Tallying of District and Electorate votes are Equal for Year 1988

```{r Ensure 1988 is okay}
# Extracting only Final District Results of 
# Number of Registered Electors
# and then adding all the votes 
ElecFinal1988<-subset(Election1988,Electorate=="Final District Results" 
                      & ColNames=="No of Registered Electors")
# added votes will be cross checked with the pdf document
ElecFinal1988[,sum(Votes),by="ColNames"]

# Extracting except Final District Results of 
# Number of Registered Electors
# and then adding all the votes 
ElecFinal1988<-subset(Election1988,Electorate!="Final District Results" 
                      & ColNames=="No of Registered Electors")
# added votes will be cross checked with the pdf document
ElecFinal1988[,sum(Votes),by="ColNames"]

# Extracting only Final District Results of 
# Total Polled
# and then adding all the votes 
ElecFinal1988<-subset(Election1988,Electorate=="Final District Results" 
                      & ColNames=="Total No of Votes Polled")
# added votes will be cross checked with the pdf document
ElecFinal1988[,sum(Votes),by="ColNames"]

# Extracting except Final District Results of 
# Total Polled
# and then adding all the votes 
ElecFinal1988<-subset(Election1988,Electorate!="Final District Results" 
                      & ColNames=="Total No of Votes Polled")
# added votes will be cross checked with the pdf document
ElecFinal1988[,sum(Votes),by="ColNames"]

# Extracting only Final District Results of 
# No of Rejected Votes
# and then adding all the votes 
ElecFinal1988<-subset(Election1988,Electorate=="Final District Results" 
                      & ColNames=="No of Rejected Votes")
# added votes will be cross checked with the pdf document
ElecFinal1988[,sum(Votes),by="ColNames"]

# Extracting except Final District Results of 
# No of Rejected Votes
# and then adding all the votes 
ElecFinal1988<-subset(Election1988,Electorate!="Final District Results" 
                      & ColNames=="No of Rejected Votes")
# added votes will be cross checked with the pdf document
ElecFinal1988[,sum(Votes),by="ColNames"]

# Extracting only Final District Results of 
# Total No of Valied Votes
# and then adding all the votes 
ElecFinal1988<-subset(Election1988,Electorate=="Final District Results" 
                      & ColNames=="Total No of Valid Votes")
# added votes will be cross checked with the pdf document
ElecFinal1988[,sum(Votes),by="ColNames"]

# Extracting except Final District Results of 
# Total No of Valied Votes
# and then adding all the votes 
ElecFinal1988<-subset(Election1988,Electorate!="Final District Results" 
                      & ColNames=="Total No of Valid Votes")
# added votes will be cross checked with the pdf document
ElecFinal1988[,sum(Votes),by="ColNames"]

# Extracting only Final District Results of 
# Mr. Ranasinghe Premadasa
# and then adding all the votes 
ElecFinal1988<-subset(Election1988,Electorate=="Final District Results" 
                      & ColNames=="Mr.Ranasinghe Premadasa")
# added votes will be cross checked with the pdf document
ElecFinal1988[,sum(Votes),by="ColNames"]

# Extracting except Final District Results of 
# Mr. Ranasinghe Premadasa
# and then adding all the votes 
ElecFinal1988<-subset(Election1988,Electorate!="Final District Results" 
                      & ColNames=="Mr.Ranasinghe Premadasa")
# added votes will be cross checked with the pdf document
ElecFinal1988[,sum(Votes),by="ColNames"]

# Extracting only Final District Results of 
# Mrs. Sirimavo Ratwatte Dias Bandaranaike
# and then adding all the votes 
ElecFinal1988<-subset(Election1988,Electorate=="Final District Results" 
                      & ColNames=="Mrs.Sirimavo Ratwatte Dias Bandaranaike")
# added votes will be cross checked with the pdf document
ElecFinal1988[,sum(Votes),by="ColNames"]

# Extracting except Final District Results of 
# Mrs. Sirimavo Ratwatte Dias Bandaranaike
# and then adding all the votes 
ElecFinal1988<-subset(Election1988,Electorate!="Final District Results" 
                      & ColNames=="Mrs.Sirimavo Ratwatte Dias Bandaranaike")
# added votes will be cross checked with the pdf document
ElecFinal1988[,sum(Votes),by="ColNames"]

# Extracting only Final District Results of 
# Mr. Oswin Abeygunasekara
# and then adding all the votes 
ElecFinal1988<-subset(Election1988,Electorate=="Final District Results" 
                      & ColNames=="Mr.Ahangama Vithanage Oswin Nandimitra Abhayagunasekara")
# added votes will be cross checked with the pdf document
ElecFinal1988[,sum(Votes),by="ColNames"]

# Extracting except Final District Results of 
# Mr. Oswin Abeygunasekara
# and then adding all the votes 
ElecFinal1988<-subset(Election1988,Electorate!="Final District Results" 
                      & ColNames=="Mr.Ahangama Vithanage Oswin Nandimitra Abhayagunasekara")
# added votes will be cross checked with the pdf document
ElecFinal1988[,sum(Votes),by="ColNames"]
```

So now the Totals have changed  and below is the final tally :

1. No of Registered Electors : 9375742
2. Total No of Valid Votes : 5094775
3. No of Rejected Votes : 91445	
4. Total No of Polled Votes : 5186277
5. Mr. Ranasinghe Premadasa : 2569199
6. Mr. Sirimavo Bandaranaike  : 2289857
7. Mr. Abeygunasekara Osvin : 235701

## Rectify Data-frame for 1999

There are no votes and percentages that needs to be rectified, only
of removing few rows. 

```{r Rectify 1999}
# Removing the Postal District Votes for No of Registered Electors rows
Election1999<-Election1999[!(Election1999$ColNames=="No of Registered Electors" & 
                             Election1999$Electorate=="Postal District Votes" & 
                             is.na(Election1999$Votes)),]
```

## Ensure if Still Tallying of District and Electorate votes are Equal for Year 1999

```{r Ensure 1999 is okay}
# Extracting only Final District Results of 
# Number of Registered Electors
# and then adding all the votes 
ElecFinal1999<-subset(Election1999,Electorate=="Final District Results" 
                      & ColNames=="No of Registered Electors")
# added votes will be cross checked with the pdf document
ElecFinal1999[,sum(Votes),by="ColNames"]

# Extracting except Final District Results of 
# Number of Registered Electors
# and then adding all the votes 
ElecFinal1999<-subset(Election1999,Electorate!="Final District Results" 
                      & Electorate!="Postal District Votes"
                      & ColNames=="No of Registered Electors")
# added votes will be cross checked with the pdf document
ElecFinal1999[,sum(Votes),by="ColNames"]

# Extracting only Final District Results of 
# Total No of Votes Polled
# and then adding all the votes 
ElecFinal1999<-subset(Election1999,Electorate=="Final District Results" 
                      & ColNames=="Total No of Votes Polled")
# added votes will be cross checked with the pdf document
ElecFinal1999[,sum(Votes),by="ColNames"]

# Extracting except Final District Results of 
# Total No of Votes Polled
# and then adding all the votes 
ElecFinal1999<-subset(Election1999,Electorate!="Final District Results" 
                      & ColNames=="Total No of Votes Polled")
# added votes will be cross checked with the pdf document
ElecFinal1999[,sum(Votes),by="ColNames"]

# Extracting only Final District Results of 
# Rejected Votes
# and then adding all the votes 
ElecFinal1999<-subset(Election1999,Electorate=="Final District Results" 
                      & ColNames=="No of Rejected Votes")
# added votes will be cross checked with the pdf document
ElecFinal1999[,sum(Votes),by="ColNames"]

# Extracting except Final District Results of 
# Rejected Votes
# and then adding all the votes 
ElecFinal1999<-subset(Election1999,Electorate!="Final District Results" 
                      & ColNames=="No of Rejected Votes")
# added votes will be cross checked with the pdf document
ElecFinal1999[,sum(Votes),by="ColNames"]

# Extracting only Final District Results of 
# Valid Votes
# and then adding all the votes 
ElecFinal1999<-subset(Election1999,Electorate=="Final District Results" 
                      & ColNames=="Total No of Valid Votes")
# added votes will be cross checked with the pdf document
ElecFinal1999[,sum(Votes),by="ColNames"]

# Extracting except Final District Results of 
# Valid Votes
# and then adding all the votes 
ElecFinal1999<-subset(Election1999,Electorate!="Final District Results" 
                      & ColNames=="Total No of Valid Votes")
# added votes will be cross checked with the pdf document
ElecFinal1999[,sum(Votes),by="ColNames"]

# Extracting only Final District Results of 
# Mrs. Chandrika Bandaranaike Kumarathunga
# and then adding all the votes 
ElecFinal1999<-subset(Election1999,Electorate=="Final District Results" 
                      & ColNames=="Chandrika Bandaranaike Kumaratunga")
# added votes will be cross checked with the pdf document
ElecFinal1999[,sum(Votes),by="ColNames"]

# Extracting except Final District Results of 
# Mrs. Chandrika Bandaranaike Kumarathunga
# and then adding all the votes 
ElecFinal1999<-subset(Election1999,Electorate!="Final District Results" 
                      & ColNames=="Chandrika Bandaranaike Kumaratunga")
# added votes will be cross checked with the pdf document
ElecFinal1999[,sum(Votes),by="ColNames"]

# Extracting only Final District Results of 
#  Mr. Ranil Wickremasinghe 
# and then adding all the votes 
ElecFinal1999<-subset(Election1999,Electorate=="Final District Results" 
                      & ColNames=="Ranil Wickramasinghe")
# added votes will be cross checked with the pdf document
ElecFinal1999[,sum(Votes),by="ColNames"]

# Extracting except Final District Results of 
#  Mr. Ranil Wickremasinghe 
# and then adding all the votes 
ElecFinal1999<-subset(Election1999,Electorate!="Final District Results" 
                      & ColNames=="Ranil Wickramasinghe")
# added votes will be cross checked with the pdf document
ElecFinal1999[,sum(Votes),by="ColNames"]

# Extracting only Final District Results of 
#  Mr.  M. D. Nandana Gunathilaka 
# and then adding all the votes 
ElecFinal1999<-subset(Election1999,Electorate=="Final District Results" 
                      & ColNames=="M.D. Nandana Gunathilaka")
# added votes will be cross checked with the pdf document
ElecFinal1999[,sum(Votes),by="ColNames"]

# Extracting except Final District Results of 
#  Mr.  M. D. Nandana Gunathilaka 
# and then adding all the votes 
ElecFinal1999<-subset(Election1999,Electorate!="Final District Results" 
                      & ColNames=="M.D. Nandana Gunathilaka")
# added votes will be cross checked with the pdf document
ElecFinal1999[,sum(Votes),by="ColNames"]

# Extracting only Final District Results of 
# Mr.  Harischandra Wijayatunga  
# and then adding all the votes 
ElecFinal1999<-subset(Election1999,Electorate=="Final District Results" 
                      & ColNames=="Harishchandra Wijayatunga")
# added votes will be cross checked with the pdf document
ElecFinal1999[,sum(Votes),by="ColNames"]

# Extracting except Final District Results of 
# Mr.  Harischandra Wijayatunga 
# and then adding all the votes 
ElecFinal1999<-subset(Election1999,Electorate!="Final District Results" 
                      & ColNames=="Harishchandra Wijayatunga")
# added votes will be cross checked with the pdf document
ElecFinal1999[,sum(Votes),by="ColNames"]

# Extracting only Final District Results of 
# Mr.  Tennyson Edirisuriya    
# and then adding all the votes 
ElecFinal1999<-subset(Election1999,Electorate=="Final District Results" 
                      & ColNames=="Tennyson Edirisuriya")
# added votes will be cross checked with the pdf document
ElecFinal1999[,sum(Votes),by="ColNames"]

# Extracting except Final District Results of 
# Mr.  Tennyson Edirisuriya   
# and then adding all the votes 
ElecFinal1999<-subset(Election1999,Electorate!="Final District Results" 
                      & ColNames=="Tennyson Edirisuriya")
# added votes will be cross checked with the pdf document
ElecFinal1999[,sum(Votes),by="ColNames"]

# Extracting only Final District Results of 
# Mr. W. V. M. Ranjith     
# and then adding all the votes 
ElecFinal1999<-subset(Election1999,Electorate=="Final District Results" 
                      & ColNames=="W.V.M. Ranjith")
# added votes will be cross checked with the pdf document
ElecFinal1999[,sum(Votes),by="ColNames"]

# Extracting except Final District Results of 
# Mr. W. V. M. Ranjith    
# and then adding all the votes 
ElecFinal1999<-subset(Election1999,Electorate!="Final District Results" 
                      & ColNames=="W.V.M. Ranjith")
# added votes will be cross checked with the pdf document
ElecFinal1999[,sum(Votes),by="ColNames"]

# Extracting only Final District Results of 
# Mr.  Rajiva Wijesinha     
# and then adding all the votes 
ElecFinal1999<-subset(Election1999,Electorate=="Final District Results" 
                      & ColNames=="Rajiva Wijesinha")
# added votes will be cross checked with the pdf document
ElecFinal1999[,sum(Votes),by="ColNames"]

# Extracting except Final District Results of 
# Mr.  Rajiva Wijesinha     
# and then adding all the votes 
ElecFinal1999<-subset(Election1999,Electorate!="Final District Results" 
                      & ColNames=="Rajiva Wijesinha")
# added votes will be cross checked with the pdf document
ElecFinal1999[,sum(Votes),by="ColNames"]

# Extracting only Final District Results of 
# Mr.  Vasudeva Nanyakkara      
# and then adding all the votes 
ElecFinal1999<-subset(Election1999,Electorate=="Final District Results" 
                      & ColNames=="Vasudeva Nanayakkara")
# added votes will be cross checked with the pdf document
ElecFinal1999[,sum(Votes),by="ColNames"]

# Extracting except Final District Results of 
# Mr.  Vasudeva Nanyakkara      
# and then adding all the votes 
ElecFinal1999<-subset(Election1999,Electorate!="Final District Results" 
                      & ColNames=="Vasudeva Nanayakkara")
# added votes will be cross checked with the pdf document
ElecFinal1999[,sum(Votes),by="ColNames"]

# Extracting only Final District Results of 
# Mr.  Abdul Rasool       
# and then adding all the votes 
ElecFinal1999<-subset(Election1999,Electorate=="Final District Results" 
                      & ColNames=="Abdul Rasool")
# added votes will be cross checked with the pdf document
ElecFinal1999[,sum(Votes),by="ColNames"]

# Extracting except Final District Results of 
# Mr.  Abdul Rasool       
# and then adding all the votes 
ElecFinal1999<-subset(Election1999,Electorate!="Final District Results" 
                      & ColNames=="Abdul Rasool")
# added votes will be cross checked with the pdf document
ElecFinal1999[,sum(Votes),by="ColNames"]

# Extracting only Final District Results of 
# Mr.  Kamal Karunadasa        
# and then adding all the votes 
ElecFinal1999<-subset(Election1999,Electorate=="Final District Results" 
                      & ColNames=="Kamal Karunadasa")
# added votes will be cross checked with the pdf document
ElecFinal1999[,sum(Votes),by="ColNames"]

# Extracting except Final District Results of 
# Mr.  Kamal Karunadasa        
# and then adding all the votes 
ElecFinal1999<-subset(Election1999,Electorate!="Final District Results" 
                      & ColNames=="Kamal Karunadasa")
# added votes will be cross checked with the pdf document
ElecFinal1999[,sum(Votes),by="ColNames"]

# Extracting only Final District Results of 
# Mr.  Alwis Weerakkody Permawardhana         
# and then adding all the votes 
ElecFinal1999<-subset(Election1999,Electorate=="Final District Results" 
                      & ColNames=="Alwis Weerakkody Premawardhana")
# added votes will be cross checked with the pdf document
ElecFinal1999[,sum(Votes),by="ColNames"]

# Extracting except Final District Results of 
# Mr.  Alwis Weerakkody Permawardhana          
# and then adding all the votes 
ElecFinal1999<-subset(Election1999,Electorate!="Final District Results" 
                      & ColNames=="Alwis Weerakkody Premawardhana")
# added votes will be cross checked with the pdf document
ElecFinal1999[,sum(Votes),by="ColNames"]

# Extracting only Final District Results of 
# Mr.  Hudson Samarasinghe         
# and then adding all the votes 
ElecFinal1999<-subset(Election1999,Electorate=="Final District Results" 
                      & ColNames=="Hudson Samarasinghe")
# added votes will be cross checked with the pdf document
ElecFinal1999[,sum(Votes),by="ColNames"]

# Extracting except Final District Results of 
# Mr.  Hudson Samarasinghe           
# and then adding all the votes 
ElecFinal1999<-subset(Election1999,Electorate!="Final District Results" 
                      & ColNames=="Hudson Samarasinghe")
# added votes will be cross checked with the pdf document
ElecFinal1999[,sum(Votes),by="ColNames"]

# Extracting only Final District Results of 
# Mr.  Ariyawansa Dissanayaka         
# and then adding all the votes 
ElecFinal1999<-subset(Election1999,Electorate=="Final District Results" 
                      & ColNames=="Ariyawansha Dissanayaka")
# added votes will be cross checked with the pdf document
ElecFinal1999[,sum(Votes),by="ColNames"]

# Extracting except Final District Results of 
# Mr.  Ariyawansa Dissanayaka           
# and then adding all the votes 
ElecFinal1999<-subset(Election1999,Electorate!="Final District Results" 
                      & ColNames=="Ariyawansha Dissanayaka")
# added votes will be cross checked with the pdf document
ElecFinal1999[,sum(Votes),by="ColNames"]
```

So now the Totals have changed  and below is the final tally :

1. No of Registered Electors : 11779200
2. Total No of Valid Votes : 8435754
3. No of Rejected Votes : 199536
4. Total No of Polled Votes : 8635290
5. Chandrika Bandaranaike Kumarathunga : 4312157
6. Ranil Wickremasinghe : 3602748
7. M. D. Nandana Gunathilaka : 344173
8. Harischandra Wijayatunga : 35854
9. W. V. M. Ranjith : 27052
10. Rajiva Wijesinha : 25085
11. Vasudeva Nanyakkara : 23668
12. Tennyson Edirisuriya : 21119
13. Abdul Rasool : 17359
14. Kamal Karunadasa : 11333
15. Hudson Samarasinghe : 7184
16. Ariyawansa Dissanayaka : 4039
17. Alwis Weerakkody Permawardhana : 3983	

# Useful Data-frames

All three data-frames look fine, now is the final stage of exporting each 
data-frame as a csv file.

```{r Export csv file}
write.csv(Election1982, file = "Election1982.csv")
write.csv(Election1988, file = "Election1988.csv")
write.csv(Election1999, file = "Election1999.csv")
```


*THANK YOu*
