---
title: "Example"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,message = FALSE,warning = FALSE,fig.width = 10,fig.height = 9)

# Load packages
library(ggplot2)
library(gganimate)
library(dplyr)
library(ggthemr)
# load data 
Final<-read.csv("Final.csv",header = TRUE)
years<-unique(Final$Year)

# Chalk theme
ggthemr("flat dark")
```

# General Votes

## No of Registered Electors and Total No of Polled Votes Over the Years

```{r Reg Electors and Polled Votes}
Final %>%
  subset(ColNames=="No of Registered Electors" & Electorate=="Final District Results" | 
         ColNames=="Total No of Votes Polled" & Electorate=="Final District Results") %>%
  group_by(Year,ColNames) %>%
  summarise(Votes=sum(Votes)/100000) %>%
ggplot(.,aes(Year,Votes,color=ColNames,label=Votes))+
       ylab("Votes (in 100,000)")+
       geom_point()+geom_line()+
       geom_text(vjust=-1,size=3)+
       scale_x_continuous(breaks = years)+
       theme(legend.position = "bottom")
```

## No of Registered Electors and Total No of Polled Votes Over the years by district

```{r Reg Electors and Polled Votes district}
Final %>%
   subset(ColNames=="No of Registered Electors" & Electorate=="Final District Results" | 
          ColNames=="Total No of Votes Polled" & Electorate=="Final District Results") %>%
ggplot(.,aes(District,Votes/10000,fill=ColNames))+
       ylab("Votes (in 10,000)")+
       geom_bar(stat = "identity",position = "dodge")+
       transition_states(factor(Year),state_length = 2)+ 
       theme(legend.position = "bottom",
             axis.text.x = element_text(angle=90,vjust=-0.1))+
       ggtitle("Year :{closest_state}")
```


## No of Rejected Votes Over the Years

```{r Rejected Votes}
Final %>%
  subset(ColNames=="No of Rejected Votes" & Electorate=="Final District Results") %>%
  group_by(Year,ColNames) %>%
  summarise(Votes=sum(Votes)/100000) %>%
ggplot(.,aes(Year,Votes,label=Votes))+
       geom_col()+geom_text(vjust=1)+
       ylab("Votes (in 100,000)")+
       scale_x_continuous(breaks = years)
```

## No of Rejected Votes Over the Years by district

```{r Rejected Votes by district}
Final %>%
  subset(ColNames=="No of Rejected Votes" & Electorate=="Final District Results") %>%
ggplot(.,aes(District,Votes/10000,label=Votes/10000))+
       geom_col()+geom_text(vjust=1,size=2)+
       ylab("Votes (in 10,000)")+
       transition_states(factor(Year),state_length = 2)+ 
       theme(legend.position = "bottom",
             axis.text.x = element_text(angle=90,vjust=-0.1))+
       ggtitle("Year :{closest_state}")
```


# Postal Votes

## Postal Votes Polled Over the Years

```{r Postal Votes Polled}
Final %>%
  subset(ColNames=="Total No of Votes Polled" & Electorate=="Postal District Votes") %>%
  group_by(Year,ColNames) %>%
  summarise(Votes=sum(Votes)/100000) %>%
ggplot(.,aes(Year,Votes,label=Votes))+
       geom_col()+geom_text(vjust=1)+
       ylab("Votes (in 100,000)")+
       scale_x_continuous(breaks = years)
```

## Postal Votes Polled Over the Years by district

```{r Postal Votes Polled by district}
Final %>%
  subset(ColNames=="Total No of Votes Polled" & Electorate=="Postal District Votes") %>%
ggplot(.,aes(District,Votes/10000,label=Votes/10000))+
       geom_col()+geom_text(vjust=1,size=2)+
       ylab("Votes (in 10,000)")+
       transition_states(factor(Year),state_length = 2)+ 
       theme(legend.position = "bottom",
             axis.text.x = element_text(angle=90,vjust=-0.1))+
       ggtitle("Year :{closest_state}")
```

## Postal Votes Registered Over the Years

```{r Postal Votes Registered}
Final %>%
  subset(ColNames=="No of Registered Electors" & Electorate=="Postal District Votes") %>%
  group_by(Year,ColNames) %>%
  summarise(Votes=sum(Votes)/100000) %>%
ggplot(.,aes(Year,Votes,label=Votes))+
       geom_col()+geom_text(vjust=1)+
       ylab("Votes (in 100,000)")+
       scale_x_continuous(breaks = years)
```

## Postal Votes Registered Over the Years by district

```{r Postal Votes Registered by district}
Final %>%
  subset(ColNames=="No of Registered Electors" & Electorate=="Postal District Votes") %>%
ggplot(.,aes(District,Votes,label=Votes))+
       geom_col()+geom_text(vjust=1,size=2)+
       ylab("Votes")+
       transition_states(factor(Year),state_length = 2)+ 
       theme(legend.position = "bottom",
             axis.text.x = element_text(angle=90,vjust=-0.1))+
       ggtitle("Year :{closest_state}")
```

## Postal Votes Rejected Over the Years

```{r Postal Votes Rejected}
Final %>%
  subset(ColNames=="No of Rejected Votes" & Electorate=="Postal District Votes") %>%
  group_by(Year,ColNames) %>%
  summarise(Votes=sum(Votes)/1000) %>%
ggplot(.,aes(Year,Votes,label=Votes))+
       geom_col()+geom_text(vjust=1)+
       ylab("Votes (in 1000)")+
       scale_x_continuous(breaks = years)
```

## Postal Votes Rejected Over the Years by district

```{r Postal Votes Rejected by district}
Final %>%
  subset(ColNames=="No of Rejected Votes" & Electorate=="Postal District Votes") %>%
ggplot(.,aes(District,Votes,label=Votes))+
       geom_col()+geom_text(vjust=1)+
       ylab("Votes")+
       transition_states(factor(Year),state_length = 2)+ 
       theme(legend.position = "bottom",
             axis.text.x = element_text(angle=90,vjust=-0.1))+
       ggtitle("Year :{closest_state}")
```

*THANK YOU*