---
title: "Final Data-Frame"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,message = FALSE)
```

# Importing the individual CSV files

7 data frames which were extracted from 7 pdf files
are now imported here, so that one complete data-frame 
of Presidential election data can be produced.

Further it is possible give suggestions on how the next 
presidential election data can be stored, processed and 
released in a more useful way than previous situations.

```{r Import Data}
# import the data frames
Election1982<-read.csv("Election1982.csv")
Election1988<-read.csv("Election1988.csv")
Election1994<-read.csv("Election1994.csv")
Election1999<-read.csv("Election1999.csv")
Election2005<-read.csv("Election2005.csv")
Election2010<-read.csv("Election2010.csv")
Election2015<-read.csv("Election2015.csv")
```

# Producing one final CSV file

Using rbind function we can produce one final complete data frame
which will include all the results for 7 presidential elections 
in Sri Lanka from 1982 to 2015.

```{r Export Data}
# combine the 7 data frames
Final<-rbind.data.frame(Election1982,Election1988,Election1994,
                        Election1999,Election2005,Election2010,
                        Election2015)
# export the data-frame
write.csv(Final,"Final.csv",row.names = FALSE)
```

# Summary Statistics for Final Data

With the help of summarytools package we can find the descriptive statistics
for the final data.

```{r Descriptive stat}
# Complete summary
summarytools::dfSummary(Final)
# Numerical Summary
summarytools::descr(Final[-1])
```

*THANK YOU*